QALY Comparisons - `r params$experiment` - `r params$intervention` - `r params$baseline`

### 2024-04-11 minos/outcomes/QALY_comparison2.Rmd
Improved QALY_comparison visualisation functions and script

require(tidyverse)
require(ggplot2)
require(knitr)
require(here)
require(MESS)
require(scales)

@@

```{r}
experiment <- params$experiment
baseline <- params$base
ints <- params$intervention
start.year <- params$start.year
# #
# experiment <- 'arc_batch_10'
# baseline <- 'baseline'
# ints <- c('25UniversalCredit', '50UniversalCredit', '75UniversalCredit', '100UniversalCredit')
# start.year <- 2020
```

@@

TESTING TEMPORARY TEMPORARY TEMPORARY TEMPORARY TEMPORARY TEMPORARY TEMPORARY 
```{r}
# base <- read.csv('qalys_base.csv')
# int <- read.csv('qalys_25All.csv')
# 
# combined <- rbind(base, int)
# 
# baseline <- 'baseline'
# intervention <- '25All'
```
TESTING TEMPORARY TEMPORARY TEMPORARY TEMPORARY TEMPORARY TEMPORARY TEMPORARY

@@

Just going to plot some things here like how many people affected by an intervention and what the mean / total boost amounts look like.

```{r}
combined.pop_boosted <- combined %>%
  group_by(year, run_id, intervention) %>%
  summarise(pop_boosted = sum(pop_boosted))

@@

ggplot(combined.pop_boosted, aes(x = year, y = pop_boosted, group = intervention, colour = intervention)) +
  geom_smooth() +
  labs(title = 'Number Individuals Receiving Intervention')

@@

>>>>

library(tidyverse)
library(ggplot2)
library(knitr)
library(here)
library(MESS)
library(scales)

@@

```{r}
experiment <- params$experiment
baseline <- params$base
ints <- params$intervention
start.year <- params$start.year
# #
#experiment <- 'default_batch_10'
# experiment <- 'default_config'
# baseline <- 'baseline'
# #ints <- c('25UniversalCredit', '50UniversalCredit', '75UniversalCredit', '100UniversalCredit')
# ints <- c('25All', '50All', '75All', '100All')
# #ints <- c('25All', '50All', '100All')
# start.year <- 2021
```

@@

TESTING TEMPORARY TEMPORARY TEMPORARY TEMPORARY TEMPORARY TEMPORARY TEMPORARY 
```{r}
# out.path <- here::here('output', 'tmp_down2/')
# 
# baseline <- 'baseline'
# ints <- c('25All', '50All', '75All', '100All')
# 
# start.year <- 2021
# 
# expts <- c(baseline, ints)
# 
# combined <- data.frame()
# for (expt in expts) {
#   data <- read.csv(paste0(out.path, expt, '_qalys.csv'))
#   combined <- rbind(combined, data)
# }
```
TESTING TEMPORARY TEMPORARY TEMPORARY TEMPORARY TEMPORARY TEMPORARY TEMPORARY

@@

## Boosted Population

```{r}
combined.pop_boosted <- combined %>%
  group_by(year, intervention, run_id) %>%
  summarise(pop_boosted = sum(pop_boosted, na.rm = TRUE))

@@

combined.pop_boosted.boxplot <- combined.pop_boosted %>%
  filter(year != start.year) %>%
  filter(intervention != baseline)

ggplot(combined.pop_boosted.boxplot, aes(x = year, y = pop_boosted, group = interaction(year, intervention), color = intervention)) +
  geom_boxplot() +
  labs(title = 'Number Individuals Receiving Intervention')

## Boost Amount

@@

```{r}
# #QALY_comparison <- function(combined, ints) {
#   
# p1 <- ggplot(data = combined, aes(x = year, y = QALYs, group = intervention, colour = intervention)) +
#   geom_smooth() +
#   labs(title = 'QALYs per year')
# print(p1)
# 
# # Now change from baseline
# combined.QALY.change <- combined %>%
#   select(run_id, year, intervention, QALYs) %>%
#   pivot_wider(names_from = 'intervention',
#               values_from = 'QALYs') %>%
#   #mutate(QALYs = .data[[int.name]] - .data[[base.name]]) %>%
#   mutate(across(all_of(ints), ~.x - .data[[baseline]], .names = "QALYs_{.col}")) %>%
#   select(run_id, year, contains('QALYs')) %>%
#   pivot_longer(cols = contains('QALYs'),
#                names_prefix = 'QALYs_',
#                names_to = 'scenario',
#                values_to = 'QALYs')
# 
# p2 <- ggplot(data = combined.QALY.change, aes(x = year, y = QALYs, group = scenario, color = scenario, fill = scenario)) +
#   geom_hline(yintercept = 0, linetype = 'dashed') +
#   geom_smooth() +
#   labs(title = 'QALY change')
# print(p2)
# 
# combined.QALY.change$year <- as.factor(combined.QALY.change$year)
# combined.QALY.change$scenario <- as.factor(combined.QALY.change$scenario)
# 
# p3 <- ggplot(data = combined.QALY.change, aes(x = year, y = QALYs, group = interaction(year, scenario), fill = scenario)) +
#   geom_boxplot() +
#   stat_summary(fun=mean, geom="line", aes(group=scenario), linetype = 'dashed')  + 
#   stat_summary(fun=mean, geom="point", aes(group=scenario))
# print(p3)
# 
# 
# 
# combined.QALY.change.confint <- combined.QALY.change %>%
#   group_by(year, scenario) %>%
#   summarise(n = n(),
#             mean_QALY_change = mean(QALYs),
#             margin = qt(0.975, df = n - 1) * (sd(QALYs) / sqrt(n)),
#             lower = mean_QALY_change - margin,
#             upper = mean_QALY_change + margin)
# 
# p4 <- ggplot(combined.QALY.change.confint, aes(x = year, y = mean_QALY_change, group = scenario, color = scenario, fill = scenario)) +  # 
#   geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.5) +
#   geom_line(aes(color = scenario), linetype = 'dashed') +
#   geom_hline(yintercept = 0, linetype = 'dashed') +
#   labs(title = 'QALY Change') +
#   xlab('Year') +
#   ylab('QALYs')
# print(p4)
# 
# 
# #}
```
